---
title: "Session 1: Cleaning, Summarizing, and Visualizing Data"
theme: cosmo
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Materials
Slides 

[session1_exercises.R](https://raw.githubusercontent.com/jmahieu/R-workshop/main/session1_exercises.R) (Right click + "Save as")

[session1_solutions.R](https://raw.githubusercontent.com/jmahieu/R-workshop/main/session_1_solutions.R) (Right click + "Save as") Only look at these after doing the exercises

[`dplyr` cheatsheet](https://github.com/rstudio/cheatsheets/blob/master/data-transformation.pdf)


## Preparation
Download the "Red Wine Quality" Data [here](https://raw.githubusercontent.com/jmahieu/R-workshop/main/data/winequality-red.csv) and save it in a local folder (Right click + "Save as"). This is the data we are going to use in the sessions. For more details about the dataset, consult the [original publication](https://www.sciencedirect.com/science/article/abs/pii/S0167923609001377?via%3Dihub)

Install the **tidyverse** and **stargazer** packages by typing the following code in the `RStudio` Console: 
```{r, eval = FALSE}
install.packages("tidyverse")
install.packages("stargazer")
#you could do this also in one line of code:
#install.packages(c("tidyverse", "stargazer"))
```