---
title: "Session 1: Cleaning, Summarizing, and Visualizing Data"
theme: cosmo
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Materials

 Slides | [HTML](https://jmahieu.github.io/R-workshop/slides_session1.html) | [PDF](https://github.com/jmahieu/R-workshop/raw/main/slides/slides_session1.pdf)
 

[Data](https://raw.githubusercontent.com/jmahieu/R-workshop/main/data/winequality-red.csv) (Right click + "Save as") Make sure that you save it as a csv file (with .csv as extension) and not as a text file (.txt)!


[session1_exercises.R](https://raw.githubusercontent.com/jmahieu/R-workshop/main/session1_exercises.R) (Right click + "Save as")

[session1_solutions.R](https://raw.githubusercontent.com/jmahieu/R-workshop/main/session_1_solutions.R) (Right click + "Save as") Only look at these after doing the exercises

[`dplyr` cheatsheet](https://github.com/rstudio/cheatsheets/blob/master/data-transformation.pdf)


## Preparation
Download the "Red Wine Quality" Data and save it in a local folder (Right click + "Save as"). Make sure that you can import the data into RStudio. For general instructions on how to import csv files, see the "Getting Started" page. Watch this [video](https://video.vu.nl/media/Importing+the+wine+quality+data+into+RStudio/1_ogskw7d1) to see how you can import the wine quality data. If you have troubles opening a new script, go to "File" > "New File"> "R Script". For more details about the dataset, consult the [original publication](https://www.sciencedirect.com/science/article/abs/pii/S0167923609001377?via%3Dihub)

Also download the session1_exercises.R file and save it in the same folder on your computer.

Install the **tidyverse** and **stargazer** packages by typing the following code in the `RStudio` Console: 
```{r, eval = FALSE}
install.packages("tidyverse")
install.packages("stargazer")
#you could do this also in one line of code:
#install.packages(c("tidyverse", "stargazer"))
```

Make sure that you can import the data into RStudio. For general instructions on how to import csv files, see the "Getting Started" page. 
Watch this [video](https://video.vu.nl/media/Importing+the+wine+quality+data+into+RStudio/1_ogskw7d1) to see how you can import the wine quality data.


## References
[R for Data Science - Data Transformation](https://r4ds.had.co.nz/transform.html)

[R for Data Science - Data Visualization](https://r4ds.had.co.nz/data-visualisation.html)